A Formal Model of Checked C

### 2023-01-16 sandp23/implementation.tex
update.

\noindent\emph{\_Mirror}: 
This qualifier makes ~\sourcerewriter copy the corresponding function into both ~\cregion and~\ucregion code such that callers from each region can invoke the corresponding copy.
This helps handle certain simple utility functions that might be called from both regions. For example, ~\code{append_string} in our evaluation of parsons\_wasm has callers from both the regions. 
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
_Mirror int append_string(_TPtr<char> buf,
const char* appendStr : itype(_Nt_array_ptr<const char>),
_TPtr<char> buf_start, size_t buf_len) {
/* Qualifier Rules:
1.) No access to global data NOT marked "const"
2.) Callees must be _Tainted or _Mirror
*/
...
}

\end{minted}
Placing ~\code{append_string} in ~\ucregion would require marking ~\code{appendStr} as tainted, thereby, requiring callers from ~\cregion to pass tainted parameter to ~\code{appendStr} at call-site. This would require either costly marshalling or making the arguments and other dependent pointers tainted, leading to over-tainting.
Similarly, placing ~\code{append_string} only in ~\cregion will make it hard for the callers in ~\ucregion as they should now use the callback mechanism to invoke~\code{append_string}.
Qualifying ~\code{append_string} with~\code{_Mirror} makes ~\sourcerewriter duplicate the function to ~\ucregion so that callers in each region will invoke their corresponding local copy, thereby, avoiding unnecessary tainting. 
"\_Mirror" enforces control-flow and data-flow compile-time semantic rules as shown above to assert region locality and exclusivity amongst between both the regions.

\noindent\emph{\_TLIB}:
This qualifier relaxes type-checking rules on non-memory modifying library functions allowing developers to use the function freely in ~\cregion.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// First, manually check the memory is in tainted region.
// if yes, then call strncpy.
if (!is_mem_in_range(t_str, t_str + n, SBX_LOW(), SBX_HIGH()))
  handle_violation();
// our type checker ignores this because 
// the above _TLIB annotation.
strncat(dst, t_str, n);
\end{minted}

In the above code, passing tainted pointer ~\code{t_str} to unqualified ~\code{strncat} is disallowed by our type-checker as it expects both the pointers to be non-tainted as we are in ~\cregion. If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use ~\code{strncat} with tainted source pointer in ~\cregion, instead of implementing the logic for string concatenation in ~\ucregion or marshalling data between the two regions.  
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
- extern char *strncat (char *__restrict __dest,
+ _TLIB extern char *strncat (char *__restrict __dest,
const char *__restrict __src, size_t __n); // In the header file
}
\end{minted}

@@

\subsection{Balance Assurance and Overhead}
\input{figures/newusecase}

>>>>

\noindent\emph{\_Mirror}: 
This qualifier permits copying the corresponding function into both ~\cregion and~\ucregion, which permits the handling of certain simple utility functions that might be called from both regions. For example, ~\code{append_string} in our evaluation of parsons\_wasm has callers from both the regions. 
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
_Mirror int append_string(_TPtr<char> buf,
const char* appendStr : itype(_Nt_array_ptr<const char>),
_TPtr<char> buf_start, size_t buf_len) {
/* Qualifier Rules:
1.) No access to global data NOT marked "const"
2.) Callees must be _Tainted or _Mirror
*/
...
}

\end{minted}
Qualifying ~\code{append_string} with~\code{_Mirror} duplicates the function in both regions,
so that calling \code{append_string} permits the avoidance of over-tainting \code{appendStr},
as \code{appendStr} can be unchecked and checked pointers in $\umode$ and $\cmode$ regions, respectively.
"\_Mirror" enforces control-flow and data-flow compile-time semantic rules as shown above to assert region locality and exclusivity amongst between both the regions. \liyi{fix the sentence.}

\noindent\emph{\_TLIB}:
This qualifier relaxes type-checking rules on library functions without memory modification allowing developers to use the function freely in ~\cregion.
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// First, manually check the memory is in tainted region.
// if yes, then call strncpy.
if (!is_mem_in_range(t_str, t_str + n, SBX_LOW(), SBX_HIGH()))
  handle_violation();
// our type checker ignores this because 
// the above _TLIB annotation.
strncat(dst, t_str, n);
\end{minted}

Passing tainted pointer ~\code{t_str} to unqualified ~\code{strncat} above is disallowed by our type-checker as it expects both the pointers to be non-tainted since we are in ~\cregion. If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use ~\code{strncat} with tainted source pointer in ~\cregion, instead of implementing the logic for string concatenation in ~\ucregion or marshalling data between the two regions.  
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
- extern char *strncat (char *__restrict __dest,
+ _TLIB extern char *strncat (char *__restrict __dest,
const char *__restrict __src, size_t __n); // In the header file
}
\end{minted}

@@

\subsection{Balance Assurance and Overhead}
\label{subsec:otherusecases}
\input{figures/newusecase}
